\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-27 paper/ms.tex
More abc talk

This approach is rarely usable in practice because the probability of
generating a dataset that matches the observed one is extremely low.
To work around this, the proposition
So the proposition $D = D_{\rm observed}$ with a logically
weaker one.

>>>>

This approach is rarely usable in practice because the probability of
generating a dataset that matches the observed one is extremely low.
To work around this, we replace the proposition
$D = D_{\rm observed}$ with a logically
weaker one (i.e. one that is implied by $D = D_{\rm observed}$ but does not
imply it). This is usually done by defining a few {\em summary statistics}
$s_1(D), s_2(D), ..., s_n(D)$, which hopefully capture most of the relevant
information in the data.
Then, a discrepancy function
$\rho$ is defined, measuring how different a simulated dataset $D$ is from
the real one $D_{\rm observed}$, in terms of the summary statistics:
\begin{align}
\rho\left(\{s_1(D), ..., s_n(D)\}; \{s_1(D_{\rm observed}), ..., s_n(D_{\rm observed})\}\right)
\end{align}
The analysis then proceeds by Monte Carlo sampling the
joint posterior for $\theta$ and $D$
conditional on the logically weaker proposition
\begin{align}
\rho\left(D; D_{\rm observed}\right) < \epsilon
\end{align}
where $\epsilon$ is some small number.
